%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV — Valeriy Grachev (v2)
% Source: data verified against pulumi-eks, ft-toolbox, generate-ci, argo* repos
% Template: https://github.com/posquit0/Awesome-CV

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[10pt, a4paper]{awesome-cv}

\geometry{left=1.2cm, top=.7cm, right=1.2cm, bottom=1.4cm, footskip=.4cm}

\definecolor{awesome}{HTML}{0D4F4A}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
% PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Valeriy}{Grachev}
\position{Head of Platform Engineering}
\address{Bangkok, Thailand{\enskip\cdotp\enskip}Remote (Open to US relocation)}

\telegram{spelendora}
\email{spelendora@gmail.com}
\homepage{spelendora.com/devops}
\linkedin{spelendora}

%-------------------------------------------------------------------------------
\begin{document}

\makecvheader[C]

\makecvfooter
  {}
  {Valeriy Grachev~~~·~~~Head of Platform Engineering}
  {\thepage}

%-------------------------------------------------------------------------------
% SUMMARY
%-------------------------------------------------------------------------------
\cvsection{About}

\begin{cvparagraph}
Run the shared platform that processed \textbf{5.2M+ institutional crypto trades in Q1 2026 alone} (\textbf{+160\% YoY transactions, +43\% YoY volume}) and \textbf{15M+ trades across 2024--2025}, serving \textbf{150+ institutional participants across 40 countries} for \href{https://finchtrade.com}{FinchTrade}, \href{https://finerymarkets.com}{Finery Markets} (\href{https://www.cnbc.com/2025/06/19/the-worlds-top-fintech-companies-2025.html}{CNBC World's Top 300 Fintech 2025}, Digital Assets; Deloitte Technology Fast 50 ME \& Cyprus 2026 winner), and an internal trading team. \textbf{Head of Platform Engineering at Finery Tech Holding}, reporting to the CEO with technical responsibility across infrastructure, security, compliance, and developer platform. \textbf{Run infrastructure as a product}: zero major outages in 2+ years on 24/7 markets, 50\% cloud cost reduction, and \textbf{DORA Elite delivery} (lead time under 6 min, MTTR under 4 min) --- two-person platform team supporting 30 engineers (1:15 leverage).
\end{cvparagraph}

%-------------------------------------------------------------------------------
% WORK EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Head of Platform Engineering}
    {Finery Tech Holding (parent of \href{https://finchtrade.com}{FinchTrade} \& \href{https://finerymarkets.com}{Finery Markets})}
    {Bangkok · Remote}
    {Nov. 2021 - Present}
    {
      \begin{cvitems}
        \item {Architected a 5-region active-active AWS/EKS footprint (\textbf{800+ pods, 100+ microservices}) delivering \textbf{zero major outages in 2+ years} on 24/7 crypto markets. Karpenter autoscaling, Kyverno-enforced RBAC, codified incident response with 15-min SEV1 SLA and per-component RTO/RPO; on-call paging provisioned as code through a custom Pulumi provider. Also authored the authentication gateway (Cognito + Lambda + KMS authorizers) --- the perimeter for institutional API traffic across all environments.}
        \item {Built an \textbf{internal developer platform (IDP)}: a single per-service manifest generates CI pipelines, pushes Helm values to GitOps, and rolls out via ArgoCD ApplicationSets, with ephemeral preview environments per branch. Evaluated Backstage and Port; built in-house due to crypto regulatory constraints.}
        \item {Cut cloud spend \textbf{50\%} through FinOps: Karpenter consolidation, spot in non-prod, Kubecost (FOCUS-aligned) for per-team attribution, an Aurora-backed cost data warehouse continuously analyzed by AI, and a custom Slack anomaly-alert bot that surfaces forgotten resources and noisy regressions with \textbf{LLM-generated explanations and remediation suggestions} delivered straight to the responsible team.}
        \item {Drove the org through \textbf{SOC 2 Type II and ISO 27001/27701 audits} as technical owner. Built MiCA-ready, DORA-aligned controls: signing isolation via AWS Nitro Enclaves, MPC custody integrations (Fireblocks, Inabit), AML/KYC pipeline integration (Sumsub) with FATF Travel Rule support, and an IAM access-governance system with periodic review campaigns, immutable audit log, and PDF evidence export for auditors.}
        \item {Shipped the internal operations monolith (FastAPI + React + Slack bot) covering 11 production feature scopes; highlights include \textbf{two production Claude integrations} (Jira daily digest + Confluence-grounded Slack knowledge-base assistant), AI-enriched alert routing via Robusta, ephemeral environment orchestration, and a release-coordination workflow. Frontline AI-augmented ops surface for the engineering org.}
        \item {\textbf{Lead a 2-person platform team supporting 30 engineers (1:15 leverage)}: hired the platform engineer myself, set the on-call rotation and SEV taxonomy, run quarterly platform-as-a-product roadmap with engineering leads, manage vendor relationships across crypto custody (Fireblocks, Inabit), fiat banking rails (ClearJunction, BCB), and AML/KYC (Sumsub). Sustains \textbf{DORA Elite delivery} (lead time under 6 min, MTTR under 4 min) on a 100+ microservice platform without headcount growth.}
        \item {\textbf{Incident commander and investigator} for security and platform incidents: lead the response from triage to root cause; cross-correlate session telemetry, WebSocket headers, VPC flow logs, and application traces to attribute attacks, profile threat actors, surface VPN/proxy and infrastructure anomalies, and produce post-mortems with prioritized remediation backlogs. Equally comfortable on availability incidents (rollbacks, failovers, runbook execution) and on adversarial cases requiring forensic depth.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Volunteer DevOps Lead (Part-Time)}
    {\href{https://helpingtoleave.org}{helpingtoleave.org}}
    {Remote}
    {Feb. 2022 - Aug. 2023}
    {
      \begin{cvitems}
        \item {Built and operated infrastructure for one of Ukraine's largest civilian evacuation organizations --- \textbf{92K+ people assisted}, \textbf{16K+ fully guided evacuations} from frontline and occupied territories. Featured by \href{https://huri.harvard.edu/news/uchitelka-rufina-bazlova-tetiana-kulykivska-russias-war-against-ukraine-bilingual}{Harvard Ukrainian Research Institute}.}
        \item {Led team of 5 DevOps engineers and coordinated with 30+ tech specialists. Core platform: Telegram bot network serving 300+ volunteers coordinating real-time evacuations across active war zones.}
        \item {Mitigated state-level DDoS attacks via AWS Shield and WAF to keep evacuation services online during active military operations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder · Head of Product \& Engineering}
    {\href{https://terminal.aidu.me/}{AIDU (terminal.aidu.me)}}
    {Remote}
    {Oct. 2020 - Nov. 2021}
    {
      \begin{cvitems}
        \item {Co-founded B2B marketplace connecting retail stores with service contractors in Kazakhstan. Built from zero to \textbf{30K+ customers} and \textbf{1.3K+ active contractors}.}
        \item {Owned architecture, GCP/Kubernetes infrastructure, hiring, delivery, and contractor payments end-to-end. Led team of 10.}
        \item {Integrated with major retail chains: Alser, Mechta, Leroy Merlin, Sulpak, DNS, Technograd --- enabling in-store service sales at checkout.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Head of Product \& Engineering (Concurrent Contract)}
    {EdTech Platform (\href{https://iidf.ru}{IIDF Portfolio})}
    {Remote}
    {Oct. 2018 - Nov. 2021}
    {
      \begin{cvitems}
        \item {Built enterprise education platform for Russia's largest startup accelerator (IIDF --- 400+ portfolio companies, 6B RUB fund). 30K+ students completed programs through the platform. Led team of 7.}
        \item {\textit{Concurrent part-time engagement alongside Fevlake (2018--2020) and AIDU (2020--2021).}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer}
    {\href{https://fevlake.com}{Fevlake.com}}
    {Moscow}
    {Oct. 2018 - Oct. 2020}
    {
      \begin{cvitems}
        \item {DevOps consultancy (Russia) delivering Kubernetes platforms and CI/CD for client engagements across fintech, e-commerce, and SaaS. Led monolith-to-microservices migrations and on-prem-to-cloud transitions.}
      \end{cvitems}
    }

\end{cventries}

%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------
\cvsection{Technical Expertise}

\begin{cvskills}
  \cvskill{Leadership \& Practice}{Platform-as-a-Product, Engineering Leadership, Hiring \& Team Building, Vendor Management, Site Reliability Engineering (SRE), FinOps, DevSecOps, Compliance Engineering, Internal Developer Platforms (IDP), GitOps, Incident Command}
  \cvskill{Crypto \& Fintech Domain}{Trading Infrastructure (OTC desks, non-custodial ECN, market-making \& arbitrage support), MPC Custody (Fireblocks, Inabit), AWS Nitro Enclaves for signing isolation, AML/KYC Pipelines (Sumsub), FATF Travel Rule}
  \cvskill{AI-Augmented Ops}{Production MCP (Model Context Protocol) servers, Claude API for Jira summarization \& Confluence-grounded knowledge-base assistant, AI-enriched alert routing via Robusta, incident.io AI Agent (triage pilot), AI-driven FinOps anomaly explanations}
  \cvskill{Compliance \& GRC}{SOC 2 Type II, ISO 27001/27701, MiCA-ready (July 2026 enforcement), DORA (Digital Operational Resilience Act), FINMA SRO (VQF), IAM access-governance with audit trail and PDF evidence export}
  \cvskill{Banking \& Settlement Rails}{Multi-jurisdiction fiat rails: ClearJunction (EUR), BCB Group (GBP), FVBank (USD), FiatRepublic, Nexpay; tier-1 exchange counterparty integrations (Kraken, Binance, Deribit, FalconX)}
  \cvskill{Cloud \& Kubernetes Platform}{Kubernetes (EKS) multi-region/multi-account, Karpenter, ArgoCD ApplicationSets, Istio Ambient, Kyverno, Velero, External Secrets Operator, CloudNativePG; AWS Aurora, Transit Gateway, Pod Identity, Shield/WAF, CloudFront}
  \cvskill{Infrastructure as Code}{Pulumi (Python, custom providers via gen-sdk), unit-tested with mocks, drift detection with Slack alerts; Terraform (legacy)}
  \cvskill{Observability \& Reliability}{OpenTelemetry, VictoriaMetrics (Prometheus-compatible), Loki, Tempo, Grafana, Robusta, Fluent Bit; SLO/SLI \& error-budget practice, DORA Elite delivery metrics (DevOps Research \& Assessment), SEV1--SEV4 taxonomy, RTO/RPO per component}
  \cvskill{Developer Platform \& CI/CD}{Self-service onboarding manifests, custom GitLab CI pipeline generator (17K LoC tests, 85\% coverage gate), Helm + ArgoCD GitOps, ephemeral environments, BuildKit remote-build caching}
  \cvskill{FinOps}{Kubecost (FOCUS-aligned), per-team attribution, anomaly-alert Slack bot with AI-generated remediation suggestions, Aurora-backed cost data warehouse}
  \cvskill{Security \& Identity}{Trivy SBOM/CVE, Semgrep, Gitleaks, Kyverno admission, Dex/OIDC federation, incident.io paging-as-code, AWS Secrets Manager}
  \cvskill{Networking}{Multi-VPC AWS with policy-driven Transit Gateway hub-and-spoke routing; dual Traefik fleets (external/internal NLB); self-hosted Headscale + embedded DERP relay (SOC2 data-residency)}
  \cvskill{Data Platform}{PostgreSQL (CloudNativePG), Redis, NATS, RabbitMQ, S3 + CloudFront}
  \cvskill{Programming}{Python (primary), Go, Bash}
\end{cvskills}

\vspace{2pt}
\textit{\small Spoken languages: English (Professional), Russian (Native), Japanese (A2/B1).}

%-------------------------------------------------------------------------------
% CERTIFICATIONS
%-------------------------------------------------------------------------------
\cvsection{Certifications}

\begin{cvhonors}
  \cvhonor
    {Certified Kubernetes Administrator (CKA)}
    {CNCF --- Cloud Native Computing Foundation}
    {}
    {2023}
\end{cvhonors}

%-------------------------------------------------------------------------------
\end{document}
